% Make sure to keep the text within the brackets and the output should turn out correct
\acknowledge{%

First of all, my most sincere gratitude goes to my advisor, Dr. Renato Figueiredo.
%
I deeply appreciate his support, encouragement, and guidance to complete my academic 
journey and this dissertation.
%
This work would not have been possible without his patience and support of my effort.
%
I have been very fortunate to have him as my advisor and mentor.\\
%
\indent I would also like to thank all the members of my advisory committee: Dr. Jos\'{e} A. B. 
Fortes, Dr. Xiaolin Li, and Dr. Ye Xia for their valuable time and interest in serving 
on my supervisory committee as well as their advice and comments, which helped improve the
quality of this dissertation.\\
%
\indent I also wish to thank my ACIS lab colleagues and staff, especially, Dr. Taewoong Choi, 
Dr. David Wolinsky, Dr. Girish Venkatasubramanian, Dr. Pierre St Juste, Dr. Kyungyong Lee, 
Jiangyan Xu, Yonggang Liu, Kyuho Jeong, Kensworth Subratie, and Dina Quinn.
%
I have had a wonderful time and enjoyed the lab atmosphere.\\
%
\indent I would also appreciate my master advisor, Dr. Keonwook Kim, for guiding me in 
building the path of my academic success and for motivating me to study abroad.
%
Also, I wish to express my thanks to my best friends, Yeosang Yoon and Jeongryul Seo for 
their moral support during my doctoral studies.\\
%
\indent My special thanks go to my parents, brother, and his family for their love and 
support, which motivated me to complete my research.
%
I could not have completed my dissertation without their support and patience.
%
I owe much them all.

}
